Cloud Manufacturing Ecosystem - Scheduling And Evolving

### 2015-10-22 beamer/intro.tex
modify the first version

\subsection{Cloud Manufacturing}
\begin{frame}{Brief Introduction}{Cloud Manufacturing}
\onslide<+->{Cloud manufacturing combines technologies such as
\begin{itemize}
\item Internet of Things
\item Cloud computing
\item Semantic Web
\item Virtualisation
\item Service-oriented technologies
\end{itemize}
}

\onslide<+->{Aims the manufacturing process to be
\begin{itemize}
\item networked
\item intelligent
\item service-oriented
\item knowledge-based
\item energy efficient
\end{itemize}}
\end{frame}

@@

\begin{frame}{Current Items}{National High-Tech. R\&D Program, China}
\textbf{Item}: \textit{Key Technologies Research on Cloud Manufacturing Platform for Group Enterprises (No. 2015AA042101)}
\begin{block}{Main Tasks}
  \begin{itemize}
  \item Business model and standard making in group enterprises;
  \item Multi-tenancy technology for on-demand useage;
  \item Platform development for enterprises (Cooperate);
  \item Application demonstration (Cooperate).
  \end{itemize}
\end{block}
\end{frame}

\begin{frame}{Current Items}{National Natural Science Fundation, China}
\textbf{Item}: \textit{BOSS based Product Manufacturing-service Modeling and Cloud Platform Guided Service-network Evolving (No. 71571161)}
\begin{block}{Main Tasks}
\begin{itemize}
\item Methodology study for standard Manufacturing-service;
\item Methodology study for Manufacturing-service evalution;
\item Optimize the matching for service and task;
\item Explore the evolution of Manufacturing-service.
\end{itemize}
\end{block}
\end{frame}

>>>>

\subsection{Cloud Manufacturing}
\begin{frame}{Brief Introduction}{Cloud Manufacturing}
\onslide<+->{Cloud manufacturing technologies including
\begin{itemize}
\item Internet of Things
\item Cloud computing
\item Semantic Web
\item Virtualisation
\item Service-oriented technologies
\end{itemize}
}
\onslide<+->{Aims the manufacturing process to be
\begin{itemize}
\item networked
\item intelligent
\item service-oriented
\item knowledge-based
\item energy efficient
\end{itemize}}
\end{frame}

\begin{frame}{Initial Results}{Cloud Manufacturing}
\only<1>{\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{figures/mainpage.png}
\caption{\href{http://mie.zju.edu.cn/cloud/}{Portal Web}}
\end{figure}}
\only<2>{
	\begin{block}{Main Component of Cloud Manufacturing prototype system}
		\begin{itemize}
			\item Platform portal system
			\item Order/Task management system
			\item Resource/Service management system
			\item Knowledgement management system
			\item Commercial application sharing system
		\end{itemize}	
	\end{block}
}
\end{frame}

@@

\begin{frame}{Current Items}{National High-Tech. R\&D Program, China}
\textbf{Foundation Item}: \textit{Key Technologies Research on Cloud Manufacturing Platform for Group Enterprises (No. 2015AA042101)}
\begin{block}{Main Tasks}
  \begin{itemize}
  \item Business model and standard formulating in group enterprises;
  \item Multi-tenancy technology for on-demand usage;
  \item Platform development for enterprises (Cooperate);
  \item Application demonstration (Cooperate).
  \end{itemize}
\end{block}
\end{frame}
\begin{frame}{Current Items}{National High-Tech. R\&D Program, China}
	\begin{figure}
		\centering
		\includegraphics[height=0.85\textheight]{figures/techrouteorange.pdf}
		\caption{Technology Roadmap}
	\end{figure}
\end{frame}

\begin{frame}{Current Items}{National Natural Science Foundation, China}
\textbf{Foundation Item}: \textit{BOSS based Product Manufacturing-service Modeling and Cloud Platform Guided Service-network Evolving (No. 71571161)}
\begin{block}{Main Tasks}
\begin{itemize}
\item Methodology study for standard Manufacturing-service;
\item Methodology study for Manufacturing-service evalution;
\item Optimize the matching for service and task;
\item Explore the evolution of Manufacturing-service.
\end{itemize}
\end{block}
\end{frame}
\begin{frame}{Current Items}{National Natural Science Foundation, China}
	\begin{figure}
		\centering
		\includegraphics[height=0.85\textheight]{figures/nsf.pdf}
		\caption{Main technical research relationship map}	
	\end{figure}
\end{frame}

### 2015-10-22 beamer/preliminary.tex
modify the first version

\subsection{Cloud Manufacturing}
\begin{frame}{Ecosystem Main Struct}{Cloud Manufacturing}
\only<1>{
	\begin{figure}
	\centering
	\includegraphics[height=0.82\textheight]{figures/platformstruct.pdf}
	\caption{Princiapl Struct of Cloud Manufacturing Ecosystem}
	\end{figure}
}
\only<2>{
	\begin{figure}
	\centering
	\includegraphics[height=0.82\textheight,viewport=40 0 450 250,clip=true]{figures/platformstruct.pdf}
	\end{figure}
}
\only<3>{
	\begin{figure}
	\centering
	\includegraphics[height=0.82\textheight,viewport=0 160 500 450,clip=true]{figures/platformstruct.pdf}
	\end{figure}
}
\end{frame}

\begin{frame}{Standardization \& Decomposition}{Service \& Task}
\onslide<+->{
	Cloud Manufacturing Ecosystem provides a platform which distributed manufacturing resources/orders gathered as resources/orders hub. 
}
\onslide<+->{
	\begin{block}{Related Methods}
	\begin{itemize}
	\item Resource Virtualization
	\item Construct Virtual Resource into Service Unit
	\item Service Standardization
	\item Order Decomposition into Tasks
	\end{itemize}
	\end{block}
}
\end{frame}

@@

\subsection{Operating Model}
\begin{frame}{Overview}{Operating Model}
\only<1>{The style the Cloud Manufacturing Ecosystem appears mainly depends on the way the operating model takes, therefore, research on features and issues in the Ecosystem would be taken within the scope of operating model we are going to set up in:
\begin{block}{Operating Model Components}
\begin{itemize}
\item Order Flow
\item User Rank
\item Platform
\end{itemize}
\end{block}}
\only<2>{\begin{figure}
\tiny\centering\resizebox{\textwidth}{!}{
\input{figures/operatingmodel.tex}}
\caption{Overview of the Operating Model}
\end{figure}}
\end{frame}

\begin{frame}{Order Flow}{Operating Model}
\only<1>{Each order appears when Users make transaction in the platform, it might then go through different paths:
\begin{figure}
\tiny\centering
\resizebox{\textwidth}{!}{\input{figures/simple_order_flow.tex}}
\caption{Simple Flow Chart of Order}
\end{figure}
}
\end{frame}

>>>>

\subsection{Cloud Manufacturing}
\begin{frame}{Ecosystem Main Structure}{Cloud Manufacturing}
\only<1>{
	\begin{figure}
	\centering
	\includegraphics[height=0.82\textheight]{figures/platformstruct.pdf}
	\caption{Princiapl Structure of Cloud Manufacturing Ecosystem}
	\end{figure}
}
\iffalse
\only<2>{
	\begin{figure}
	\centering
	\includegraphics[height=0.82\textheight,viewport=40 0 500 250,clip=true]{figures/platformstruct.pdf}
	\end{figure}
}
\only<3>{
	\begin{figure}
	\centering
	\includegraphics[height=0.82\textheight,viewport=0 160 500 450,clip=true]{figures/platformstruct.pdf}
	\end{figure}
}
\fi
\end{frame}

\begin{frame}{Service Standardization}{Cloud Manufacturing}
\begin{figure}
\centering
\includegraphics[height=0.85\textheight]{figures/boss.pdf}
\caption{Standard Service Tree Illustration}
\end{figure}
\iffalse
\onslide<+->{
	Cloud Manufacturing Ecosystem provides a platform which distributed manufacturing resources/orders gathered as resources/orders hub. 
}
\onslide<+->{
	\begin{block}{Related Methods}
	\begin{itemize}
	\item Resource Virtualization
	\item Construct Virtual Resource into Service Unit
	\item Service Standardization
	\item Order Decomposition into Tasks
	\end{itemize}
	\end{block}
}
\fi
\end{frame}

@@

\subsection{Operating Model}
\begin{frame}{Overview}{Operating Model}
\only<1>{The style the Cloud Manufacturing Ecosystem appears mainly depends on the way the operating model takes, therefore, research on features and issues in the Ecosystem would be taken within the scope of operating model we are going to set up in:
\begin{block}{Operating Model Components}
\begin{itemize}
\item Order Flow
\item User Rank
\item Platform
\end{itemize}
\end{block}}
\only<2>{\begin{figure}
\tiny\centering\resizebox{\textwidth}{!}{
\input{figures/sellerflow.tex}}
\caption{Seller Flow in Operating Model}
\end{figure}}
\only<3>{\begin{figure}
\tiny\centering\resizebox{\textwidth}{!}{
\input{figures/buyerflow.tex}}
\caption{Buyer Flow in Operating Model}
\end{figure}}
\end{frame}

\begin{frame}{Order Flow}{Operating Model}
\only<1>{Each order appears when Users make transaction in the platform, it might then go through different paths:
\begin{figure}
\tiny\centering
%\resizebox{\textwidth}{!}{\input{figures/order_flow.tex}
\includegraphics[height=0.9\textheight,angle=90]{figures/orderflow.pdf}
%}
\caption{Simple Flow Chart of Order}
\end{figure}
}
\end{frame}

### 2015-10-22 figures/platformstruct.tex
modify the first version

% !TEX root = ..\Eco-Model.tex
\begin{tikzpicture}
[mindmap,
every node/.style={concept, text=white, execute at begin node=\hskip0pt,circular drop shadow},
root concept/.append style={concept color=black, fill=white, line width=1ex, text=black, font=\Large\scshape},
grow cyclic,
level 1/.append style={level distance=4.5cm,sibling angle=90, font=\scshape},
level 2/.append style={level distance=3cm,sibling angle=45, font=\scriptsize\bf},
level 3/.append style={level distance=2cm,sibling angle=60, font=\scriptsize\bf},
level 4/.append style={level distance=1cm,sibling angle=60, font=\tiny\bf}]
\node [root concept] {Cloud Manufacturing Ecosystem}  % root
child [concept color = gray]{ node {Schedule}
child { node {Recommand System}}
child { node {Decision Making Support}}
child { node {Ranking Schema}}
child { node {Match Regualtion}}
}
child [concept color = gray]{ node {User}
  child { node {Submit Order}}
  child { node {Provide Resource}}
  child { node {Make Transaction}}
  child { node {Evalute Others}}
  }
child [concept color = gray]{ node {Envolve}
  child { node {Optimization}
    child { node {Manufacturing}}
    child { node {Industrial Chain}}
    }
  child { node {Member}
    child { node {Introduce}}
    child { node {Eliminate}}
    }
  child { node {Adjust User Proportion}}
  child { node {Development Guidance}}
  }
child [concept color = gray]{ node {Platform}
  child { node {Authority Control}}
  child { node {Transaction Bridge}}
  child { node {Dashbord}
    child { node {Service}}
    child { node {Task}}
    child { node {User}}
    }
  child { node {Administrate}}
  child { node {Hub}
    child { node {Service}}
    child { node {Resource}}
    child { node {Ranking}}
    }
  }
;
\end{tikzpicture}

>>>>

% !TEX root = ..\Eco-Model.tex
\begin{tikzpicture}
[mindmap,
every node/.style={concept, text=white, execute at begin node=\hskip0pt,circular drop shadow},
root concept/.append style={concept color=black, fill=white, line width=1ex, text=black, font=\Large\scshape},
grow cyclic,
level 1/.append style={level distance=4.5cm,sibling angle=90, font=\scshape},
level 2/.append style={level distance=3cm,sibling angle=45, font=\scriptsize\bf},
level 3/.append style={level distance=2cm,sibling angle=60, font=\scriptsize\bf},
level 4/.append style={level distance=1cm,sibling angle=60, font=\tiny\bf}]
\node [root concept] {Cloud Manufacturing Ecosystem}  % root
child [concept color = gray]{ node {Schedule}
child { node {Service Standardization}}
child { node {Decision Making Support}}
child { node {Platform Assistance}}
child { node {Match Regualtion}}
}
child [concept color = gray]{ node {User}
  child { node {Seller}
    child { node {Provide Resources}}
    child { node {Schedule Orders}}
    child { node {Outsource Orders}}
    child { node {Evaluate Buyer}}
  }
  child
  child { node {Buyer}
    child { node {Submit Order}}
    child { node {Choose Seller}}
    child { node {Evaluate Seller}}
  }
  }
child [concept color = gray]{ node {Evolve}
  child { node {Optimization}
    child { node {Manufacturing}}
    child { node {Industrial Chain}}
    }
  child { node {Member}
    child { node {Introduce}}
    child { node {Eliminate}}
    }
  child { node {Adjust User Proportion}
    child { node {Rating}}
    child { node {Recommand}}
    }
  child { node {Development Guidance}}
  }
child [concept color = gray]{ node {Platform}
  child { node {Authority Control}}
  child { node {Transaction Bridge}}
  child { node {Dashbord}
    child { node {Service}}
    child { node {Task}}
    child { node {User}}
    }
child { node {Administrate}}
  child { node {Hub}
    child { node {Service}}
    child { node {Resource}}
    child { node {Ranking}}
    }
  child { node {Scheduling Assistance}}
}
;
\end{tikzpicture}
